---
title       : Diamonds Are Forever
subtitle    : Exploring Diamonds Dataset
author      : Ewa Wesolowska
job         : Coursera Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]  # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 

<style>
article p {
  font-size: 16px;
}
article code {
  font-size: 14px;
}

</style>

### The diamonds dataset

The 'Diamonds are Forever' application explores the diamond dataset available with R Package ggplot2.
This dataset was built using slidify and hosted on shinyapp.io as [Diamonds Are Forever](https://ewat3ch.shinyapps.io/diamonds_are_forever/). The application compares the price, cut, carat and clarity of almost 54,000 diamonds. 

```{r}
library(ggplot2)
str(diamonds)
```

--- 

### What carat value of diamond can I get ?

Having chosen either the price, cut or clarity, the application will plot the available diamonds carat within those parameters.

<img height='500' width='700' src=img-week4/diamonds_are_forever.png>

---  &checkbox

### Quizz

```{r, echo=FALSE, message=FALSE, results='hide'}
library(dplyr)
cut_list <- list(unique(diamonds$cut))

diamonds_under_2500_price <- diamonds %>% filter(price <= 2500)
#fair_cnt <- diamonds_2500_price %>% count(cut,sort=TRUE) %>% filter(cut=='Fair')
#fcmean <- diamonds_2500_price %>% filter(cut=='Fair') %>% summarise(mean=mean(carat))
#good_cnt <- diamonds_2500_price %>% count(cut,sort=TRUE) %>% filter(cut=='Good')
#fcmean <- diamonds_2500_price %>% filter(cut=='Good') %>% summarise(mean=mean(carat))
#very_good_cnt <- diamonds_2500_price %>% count(cut,sort=TRUE) %>% filter(cut=='Very Good')
#fcmean <- diamonds_2500_price %>% filter(cut=='Very Good') %>% summarise(mean=mean(carat))
#premium <- diamonds_2500_price %>% count(cut,sort=TRUE) %>% filter(cut=='Premium')
#fcmean <- diamonds_2500_price %>% filter(cut=='Premium') %>% summarise(mean=mean(carat))
#ideal_cnt <- diamonds_2500_price %>% count(cut,sort=TRUE) %>% filter(cut=='Ideal')
#fcmean <- diamonds_2500_price %>% filter(cut=='Ideal') %>% summarise(mean=mean(carat))
#summarize(mean_price=mean(price), mean_carat=mean(carat))

```

James is planning to ask his girlfriend Linda to marry him with a diamond ring. 
Having `$2,500` in his savings account, can James still buy the 'ideal' diamond for Linda?

The available price range for James' diamond is from the lowest price `$326` to `$18,823`, with the quality of either:Fair, Good, Very Good or Premium.

1. _Yes_
2. No

*** .hint

Does carat matter ?

*** .explanation

YES! However, in the diamond data set the low carat will be  0.437 and the highest being 5.01.

--- &twocol

### How many diamonds and their clarity are available under the `$2500` dollar mark ? 

*** =left

```{r, fig.align = 'left'}
ggplot(data = diamonds_under_2500_price) + 
  geom_bar(mapping = aes(x = cut, fill = clarity), 
           position = "dodge")
```

*** =right

```{r, fig.align = 'right'}
ggplot(diamonds_under_2500_price, 
       aes(carat, price, color=clarity)) + 
       geom_point() 
```

*** =fullwidth
